Negative Perceptions of Outsourcing to Artificial Intelligence

### 2025-04-22 appendix.qmd
Start preparing supplementary materials

# **Supplementary Materials**

\setcounter{page}{1}
\begin{center}
Negative Perceptions of Outsourcing to Artificial Intelligence \\
Scott Claessens, Pierce Veitch, and Jim Everett \\
School of Psychology, University of Kent
\end{center}
\newpage

@@

We pre-registered the study on the Open Science Framework
([https://osf.io/khr42](https://osf.io/khr42)).

@@

Frequency lists were created with the *Frequency List* plugin (Version 1.0.11). 
Settings included: unigram analysis (N = 1), omission of n-grams with frequency
< 5, exclusion of n-grams appearing in fewer than 0.1% of documents, filtering 
collocates by Normalized Pointwise Mutual Information, and removal of collocates 
with metric values < 0.5. Outputs were saved using the *Save Output to CSV* 
plugin (Version 1.0.5). This process was repeated separately for each condition 
folder.

@@

Boyd, R. L. (2019). BUTTER: Basic unit-transposable text experimentation 
resource. Available from https://www.butter.tools/

Gregson, R., Piazza, J., & Boyd, R. L. (2022). 'Against the cult of veganism': Unpacking the social psychology and ideology of anti-vegans. *Appetite*, *178*, 106143. doi:10.1016/j.appet.2022.106143

Rayson, P., & Garside, R. (2000). Comparing corpora using frequency profiling. *Proceedings of the Workshop on Comparing Corpora - Volume 9*, 1–6. Presented in Hong Kong. doi:10.3115/1117729.1117730

>>>>

# Supplementary Materials {.unnumbered .unlisted}

\setcounter{page}{1}
\begin{center}
Negative Perceptions of Outsourcing to Artificial Intelligence \\
Scott Claessens, Pierce Veitch, and Jim Everett \\
School of Psychology, University of Kent
\end{center}
\newpage
\tableofcontents
\newpage

@@

We pre-registered the study on the Open Science Framework
(<https://osf.io/khr42>).

@@

Frequency lists were created with the *Frequency List* plugin (Version 1.0.11). 
Settings included: unigram analysis (N = 1), omission of n-grams with frequency
< 5, exclusion of n-grams appearing in fewer than 0.1% of documents, filtering 
collocates by Normalized Pointwise Mutual Information (NPMI), and removal of 
collocates with metric values < 0.5. Outputs were saved using the 
*Save Output to CSV* plugin (Version 1.0.5). This process was repeated 
separately for each condition folder.

@@

\setlength{\parindent}{-20pt}
\setlength{\leftskip}{20pt}

Boyd, R. L. (2019). BUTTER: Basic unit-transposable text experimentation 
resource. Available from <https://www.butter.tools/>

Gregson, R., Piazza, J., & Boyd, R. L. (2022). 'Against the cult of veganism': 
Unpacking the social psychology and ideology of anti-vegans. *Appetite*, *178*,
106143. doi:[10.1016/j.appet.2022.106143](https://doi.org/10.1016/j.appet.2022.106143)

Rayson, P., & Garside, R. (2000). Comparing corpora using frequency profiling.
*Proceedings of the Workshop on Comparing Corpora - Volume 9*, 1–6. Presented in
Hong Kong. doi:[10.3115/1117729.1117730](https://doi.org/10.3115/1117729.1117730)
